---
title: "Measurement Invariance Across Administrations"
author: "KN and MA"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: 
   word_document:
        toc: yes
        toc_depth: 2
        reference_docx: "Markdown Template.docx"
   html_document:
        toc: yes
        toc_depth: 2
---

```{r, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, results = "asis", warning = FALSE, message = FALSE)
flextable::set_flextable_defaults(fonts_ignore = TRUE)

library(dplyr)
library(flextable)
library(ggplot2)

#### Formatting Output Tables ####
format_flex <- function(df, digits = 2){
  
  if(!("flextable" %in% class(df))){
  
  numericcols <- which(unlist(lapply(df, is.numeric)))
  
  ftab <- flextable::flextable(df)
  ftab <- flextable::colformat_double(ftab, j = numericcols, digits = digits)
  } else{
    ftab <- df
  }
  ftab <- flextable::font(ftab, fontname = "Times New Roman", part = "all")
  ftab <- flextable::padding(ftab, padding = 0, part = "all")
  ftab <- flextable::align(ftab, align = "center", part = "all")
  ftab <- flextable::align(ftab, j = 1, align = "left")
  
  
  ftab <- flextable::autofit(ftab)
  # ftab <- flextable::fit_to_width(ftab, width)
  
  return(ftab)
}

## loading data

# load("MI_Results.RData")
load("MI_Results_L12.RData")
load("MI_Results_L3.RData")
load("MI_Output.RData")

g5.results.list <- list(`Commitment to Learning (CTL)` = g5.ctl.results,
                        `Positive Identity and Outlook (PIO)` = g5.pio.results,
                        `Social Competence (SC)` = g5.sc.results,
                        # `Empowerment (EMP)` = g5.emp.results,
                        `Family/Community Support (FCS)` = g5.fcs.results,
                        `Teacher/School Support (TSS)` = g5.tss.results)

g8.results.list <- list(`Commitment to Learning (CTL)` = g8.ctl.results,
                        `Positive Identity and Outlook (PIO)` = g8.pio.results,
                        `Social Competence (SC)` = g8.sc.results,
                        # `Empowerment (EMP)` = g8.emp.results,
                        `Family/Community Support (FCS)` = g8.fcs.results,
                        `Teacher/School Support (TSS)` = g8.tss.results)

g9.results.list <- list(`Commitment to Learning (CTL)` = g9.ctl.results,
                        `Positive Identity and Outlook (PIO)` = g9.pio.results,
                        `Social Competence (SC)` = g9.sc.results,
                        # `Empowerment (EMP)` = g9.emp.results,
                        `Family/Community Support (FCS)` = g9.fcs.results,
                        `Teacher/School Support (TSS)` = g9.tss.results)

g11.results.list <- list(`Commitment to Learning (CTL)` = g11.ctl.results,
                        `Positive Identity and Outlook (PIO)` = g11.pio.results,
                        `Social Competence (SC)` = g11.sc.results,
                        # `Empowerment (EMP)` = g11.emp.results,
                        `Family/Community Support (FCS)` = g11.fcs.results,
                        `Teacher/School Support (TSS)` = g11.tss.results)
```

# Demographics

**Supplemental Table 1.**

*Student Characteristics by Year*

```{r, eval = FALSE}
format_flex(demos.year)
```

**Supplemental Table 2.**

*Student Characteristics by Grade*

```{r, eval = FALSE}
format_flex(demos.grade)
```

# Grade 5

```{r}

for(i in 1:length(g5.results.list)){
 cat("##", names(g5.results.list)[[i]])
 cat("\n\n")
 cat("*Model fit for each model and model comparison statistics*")
 cat("\n\n")
 format_flex(g5.results.list[[i]]$Fits) %>% knitr::knit_print() %>% cat()
 cat("\n\n")
 cat("*Unstandardized factor loadings for each group and constrained*")
 cat("\n\n")
 format_flex(g5.results.list[[i]]$Loadings) %>% knitr::knit_print() %>% cat()
 cat("\n\n")
 cat("*Standardized means and unstandardized variances after constraining thresholds and loadings*")
 cat("\n\n")
 format_flex(g5.results.list[[i]]$Means_Vars) %>% knitr::knit_print() %>% cat()
 cat("\n\n")
 if(!is.null(g5.results.list[[i]]$Partial)){
    cat("*Investigating parameters to release for partial invariance*")
    cat("\n\n")
    r <- min(15, nrow(g5.results.list[[i]]$Partial))
    format_flex(g5.results.list[[i]]$Partial[1:r,]) %>% knitr::knit_print() %>% cat()
    cat("\n\n")    
 }
 cat("\\newpage")
}

```

# Grade 8

```{r}

for(i in 1:length(g8.results.list)){
 cat("##", names(g8.results.list)[[i]])
 cat("\n\n")
 cat("*Model fit for each model and model comparison statistics*")
 cat("\n\n")
 format_flex(g8.results.list[[i]]$Fits) %>% knitr::knit_print() %>% cat()
 cat("\n\n")
 cat("*Unstandardized factor loadings for each group and constrained*")
 cat("\n\n")
 format_flex(g8.results.list[[i]]$Loadings) %>% knitr::knit_print() %>% cat()
 cat("\n\n")
 cat("*Standardized means and unstandardized variances after constraining thresholds and loadings*")
 cat("\n\n")
 format_flex(g8.results.list[[i]]$Means_Vars) %>% knitr::knit_print() %>% cat()
 cat("\n\n")
 if(!is.null(g8.results.list[[i]]$Partial)){
    cat("*Investigating parameters to release for partial invariance*")
    cat("\n\n")
    r <- min(15, nrow(g8.results.list[[i]]$Partial))
    format_flex(g8.results.list[[i]]$Partial[1:r,]) %>% knitr::knit_print() %>% cat()
    cat("\n\n")    
 }
 cat("\\newpage")
}

```

# Grade 9

```{r}

for(i in 1:length(g9.results.list)){
 cat("##", names(g9.results.list)[[i]])
 cat("\n\n")
 cat("*Model fit for each model and model comparison statistics*")
 cat("\n\n")
 format_flex(g9.results.list[[i]]$Fits) %>% knitr::knit_print() %>% cat()
 cat("\n\n")
 cat("*Unstandardized factor loadings for each group and constrained*")
 cat("\n\n")
 format_flex(g9.results.list[[i]]$Loadings) %>% knitr::knit_print() %>% cat()
 cat("\n\n")
 cat("*Standardized means and unstandardized variances after constraining thresholds and loadings*")
 cat("\n\n")
 format_flex(g9.results.list[[i]]$Means_Vars) %>% knitr::knit_print() %>% cat()
 cat("\n\n")
 if(!is.null(g9.results.list[[i]]$Partial)){
    cat("*Investigating parameters to release for partial invariance*")
    cat("\n\n")
    r <- min(15, nrow(g9.results.list[[i]]$Partial))
    format_flex(g9.results.list[[i]]$Partial[1:r,]) %>% knitr::knit_print() %>% cat()
    cat("\n\n")    
 }
 cat("\\newpage")
}

```


# Grade 11

```{r}

for(i in 1:length(g11.results.list)){
 cat("##", names(g11.results.list)[[i]])
 cat("\n\n")
 cat("*Model fit for each model and model comparison statistics*")
 cat("\n\n")
 format_flex(g11.results.list[[i]]$Fits) %>% knitr::knit_print() %>% cat()
 cat("\n\n")
 cat("*Unstandardized factor loadings for each group and constrained*")
 cat("\n\n")
 format_flex(g11.results.list[[i]]$Loadings) %>% knitr::knit_print() %>% cat()
 cat("\n\n")
 cat("*Standardized means and unstandardized variances after constraining thresholds and loadings*")
 cat("\n\n")
 format_flex(g11.results.list[[i]]$Means_Vars) %>% knitr::knit_print() %>% cat()
 cat("\n\n")
 if(!is.null(g11.results.list[[i]]$Partial)){
    cat("*Investigating parameters to release for partial invariance*")
    cat("\n\n")
    r <- min(15, nrow(g11.results.list[[i]]$Partial))
    format_flex(g11.results.list[[i]]$Partial[1:r,]) %>% knitr::knit_print() %>% cat()
    cat("\n\n")    
 }
 cat("\\newpage")
}

```

# Manuscript Output

*Table 1. Model Fit and Comparison Statistics for Grade 5*

```{r}
format_flex(g5.table) %>% knitr::knit_print()
```

\newpage

*Table 2. Model Fit and Comparison Statistics for Grade 8*

```{r}
format_flex(g8.table) %>% knitr::knit_print()
```

\newpage

*Table 3. Model Fit and Comparison Statistics for Grade 9*

```{r}
format_flex(g9.table) %>% knitr::knit_print()
```

\newpage

*Table 4. Model Fit and Comparison Statistics for Grade 11*

```{r}
format_flex(g11.table) %>% knitr::knit_print()
```

\newpage

*Figure 1. Standardized Mean Difference Across Administrations by Grade and Measure*

```{r, eval = FALSE, fig.width = 12, fig.height = 8}
print(smd.plot)
```

*Note.* The 2016 administration of Positive Identity and Outlook is the reference year for Grade 5 as the 2013 administration used different items and was excluded from the analysis.


\newpage

*Figure 1. Standardized Mean Difference Across Administrations by Grade and Measure*

```{r, fig.width = 12, fig.height = 8}
print(smd.line)
```

*Note.* The 2016 administration of Positive Identity and Outlook is the reference year for Grade 5 as the 2013 administration used different items and was excluded from the analysis.