---
title: "Data Pipeline"
output:
  html_document:
    self_contained: no
---

This document allows running your full analysis, in concise code: the nitty-gritty details should be handled by your functions, not in this document.


# Gather
This step of the analysis is where you gather the data files used in your analysis.  
```{r gather}
source("0_general_functions.R")
source("1_gather/gather_functions.R")

## Replace {GATHER_OBJECTS} with the R objects you created in this phase
save(TheColorCards,TheCorIncCards,NotAllDeckCards,NotCards,ThePiles,
     Exam123,FinalExam,IDGroups,
     file = "1_gather/gathered.Rdata")

# save session info
session_to_file("1_gather/gather_session_info.txt")

```


# Analyze
This is where you actually calculate descriptives and fit models.  All model objects should be saved so that you can present them in different possible ways in the "present" step.
```{r analyze}
source("0_general_functions.R")
load("1_gather/gathered.Rdata")

source("3_analyze/analyze_functions.R")

save(
  # Final Exam Objects
     FESemesterDensityPlot,FEICDensityPlot,FEItemPlot,  # Descriptive plots
     FinalExam,FinalExamScores,FEItemData,              # Dataframes
     FE.lm,FEModelCheck,FEcoefs,                        # Regression
  # Pile-Level Objects
     ThePiles,PileDescrips,FunctionPilesPlot,TotalPilesPlot, # Dataframes and Descriptive plots
     TotPiles.pre,PerFunc.pre,SLcoefs,                      # Regression
     TotPilesModelPlots, PerFuncModelPlots,TotalPilesDistPlot,FunctionPilesDistPlot,
     # TotPiles.unc,TotPiles.lmer,TotPiles.lm,
     # PerFunc.unc,PerFunc.lmer,PerFunc.lm,PileMultiRegdata,TPPFResults,
  # Free Sort Total Score Objects
     TheColorCards,GroupFreq,ICSummary,SummaryPropPlot,
     # GroupFreqWide,GroupPropWide,SummaryFreqWide,SummaryPropWide, # I don't end up using the wide format data at all
     TotalScoreDescriptives,TotalScorePlot,
     # TotScoreRegdata,TotScore.unc,TotScore.lmer,TotScore.lm,TotScoreHLMResults,
     # TotScorePreTtest,TotScorePostTtest,TotScoreChangeTtest,
     TotScoreWide,TotScore.pre,TScoefs,TotScoreModelCheck,
  # Free Sort Card-level objects
     CardScoreDiff,SummaryScoreDiff,ScoreDiffPlot,CardFreqPlot,#CardCV,CardCVPlot,
  # Directed Sort Total Score Objects
     TheCorIncCards,TotScore18Summary,PrePost18DistPlot,TotScore18SummaryWide,TotScore18ttest,TotScore18wctest,
  # Directed Sort Card-level objects
     Card18Difficulty,Card18scatterCategory,Card18scatterPile,
     file = "3_analyze/analyzed.Rdata")


# save session info
session_to_file("3_analyze/analyze_session_info.txt")

```

# Present
This is where you generate reports.  This should be done by calling the "render" function on your Rmd or Rnw file, which is in the "04_present/" folder.
```{r present}
# source("0_general_functions.R")
## Code for calling render() functions on any Rmd files (all stored in '04_present/'
## folder)


```

